MADA Project: Supplemental Material

### 2021-11-28 products/manuscript/Manuscript.Rmd
MADA project part 5 (no references yet)

---
title: "MADA Project Manuscript"
subtitle: ""
author: Dawson Dobash
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

@@

https://data.oecd.org/healthres/health-spending.htm

https://www.kaggle.com/iamsouravbanerjee/covid19-dataset-world-and-continent-wise?select=Covid+Data+-+World.csv

https://www.kaggle.com/anandhuh/latest-worldwide-vaccine-data

https://data.worldbank.org/indicator/NY.GDP.PCAP.CD

https://en.wikipedia.org/wiki/List_of_countries_by_system_of_government

@@

## Full analysis

### Difference in proportions of recovery and deaths

Table 1.1 displays the top five and bottom five death rates. Also within this, it shows their corresponding recovery rates as well. We can see that the bottom five death rates are from Asia but also the highest, Yemen, is also within the Asia continent as well.

Table 1.1
```{r table1,  echo=FALSE}
tab1=readRDS("../../results/table3.rds")
knitr::kable(tab1)
```

@@

```{r figure 1.1,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/prop_diff_recov_died.png")
```

@@

```{r figure 1.2,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/log_prop_diff_hist.png")
```

@@

Using the logit transformation, I ran 4 simple linear regression models. Below I provide the statistics of each of the models within Tables 1.2-1.5.

@@

Table 1.2
```{r table 1.2,  echo=FALSE}
tab2=readRDS("../../results/tablevacc1.rds")
knitr::kable(tab2)
```

Table 1.3 is showing statistics for the predictor health care funds.

Table 1.3
```{r table 1.3,  echo=FALSE}
tab3=readRDS("../../results/tablehc1.rds")
knitr::kable(tab3)
```

Table 1.4 is showing statistics for the predictor number of tests per person.

Table 1.4
```{r table 1.4,  echo=FALSE}
tab4=readRDS("../../results/tabletests1.rds")
knitr::kable(tab4)
```

Table 1.5 is showing statistics for the predictor location which specifies the continent for each country.

Table 1.5
```{r table 1.5,  echo=FALSE}
tab5=readRDS("../../results/tableloc1.rds")
knitr::kable(tab5)
```

Looking at all of these tables, we can see that the R^2 values are very low. Therefore none of these predictors shows any association with the logit transformation outcome. Since not even one predictor is good for this outcome, I am going to stop my analysis with this outcome and go to my second question which uses the percent of cases within each country.

### Percent of people vaccinated for each country

#### Methods

@@

#### Exploratory Analysis

@@

Table 2.1
```{r table 2.1,  echo=FALSE}
tab21=readRDS("../../results/vacc_tab.rds")
knitr::kable(tab21)
```

@@

```{r figure 2.1,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/vacc_hist.png")
```

Figure 2.2 shows that there is no trend between vaccinations and cases until you get out to over 10% of the population had cases of COVID-19. The vaccination numbers range a lot when there is a low perecentage of cases compared to the countries population.

```{r figure 2.2,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/cases_vs_vacc.png")
```

When looking at Figure 2.3, we can see that those countries who have large values of GDP per capita, their population is more vaccinated. The vaccination number, just like in Figure 2.2, varies when the GDP per capita is relatively low.

```{r figure 2.3,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/gdp_vs_vacc.png")
```

Looking at Figure 2.4, this side-by-side boxplot shows that Africa is significantly different to all of the other continents. Africa is historically known is a less developed continent. This could be result in lower supplies to Africa compared to other places in the world. Within the other continents, Europe seems to have th highest median vaccinated proportions.

```{r figure 2.4,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/loc_vs_vacc.png")
```

Figure 2.5 is showing the logit transformation of the proportion of the population vaccinated. This is due to the skewness of the non-transformed vaccinatio numbers. We see that this is still skewed but its skewed left where most of the data is around that 0 value.

```{r figure 2.5,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/log_vacc.png")
```

#### Main Analysis

As specified within the methods section, the first part of my analysis will be comparing the RMSE of my full model to the null model. However, before I do this I will run a correlation matrix of the numberic variables to see if some variables are highly correlated.

In Table 2.2 we can see that the two variable, which I suspected, that are highly correlated are health care funds and GDP per capita where value is the health care fund variable. Since those two variables are highly correlated and the health care funds variable only includes 48 observations, I will remove health care funds out of the full model.

Table 2.2
```{r table 2.2,  echo=FALSE}
tab22=readRDS("../../results/cor_tab.rds")
knitr::kable(tab22)
```

@@

Table 2.3
```{r table 2.3,  echo=FALSE}
tab23=readRDS("../../results/Summ_stat_mult_reg.rds")
knitr::kable(tab23)

@@

Table 2.4
```{r table 2.4,  echo=FALSE}
tab24=readRDS("../../results/Logit_vacc_rmse_tab.rds")
knitr::kable(tab24)
```

Table 2.5
```{r table 2.5,  echo=FALSE}
tab25=readRDS("../../results/Logit_vacc_rmse_null_tab.rds")
knitr::kable(tab25)
```

@@

For the LASSO model, there is some preparation we need to run this. We will use cross validation to create the multiple models included in the LASSO model. This cross validation will be a 5-fold stratified by the outcome. We then, like previously, create a workflow using a specific model type and recipe. The recipe will be the full model recipe but the model type will be different. The LASSO model uses a specific model that has a tuning factor into a linear regression type. Once we have our workflow, we need to make a grid as the LASSO model created multiple models based on the 5-fold cross validation and other factors. From the workflow, we can apply a tuning grid to it. This will produce the variety of models. To find the best model, we an apply a function called show_best and specify RMSE to find the best model in terms of RMSE. After putting this model into a workflow and creating a fit object, we get the statistics of the best model. Figure 2.6 shows the tuning process in a visual. The best model is represented by the lowest RMSE within the dip.

```{r figure 2.6,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/lasso_tune_process.png")
```

Figure 2.7 shows the predicted values to the observed values. Most of the points follow the trend and there seems to show no pattern. We can see this more within Figure 2.8 which is the residual plot. Within Figure 2.8, we could see a slight pattern at the begging points where they are grouped up more.

```{r figure 2.7,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/Pred_vs_obs_value_lasso_train.png")
```

```{r figure 2.8,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/Resid_lasso_train.png")
```

The last part of the LASSO modeling analysis is fitting the model to the test data to see how well they both look together. To look at the test data results, we need to run a last fit function which just applies the test data to the best model found above. Figure 2.9 and Figure 2.10 show the predicted values versus observed and its residual plot for the test data. Just like the training test, most of the predicted values do have a similar trend and it close to the observed value. The residual plot shows that concerning line of observations for the lower values. This residual plot show more variability in the lower values more. Table 2.6 shows the RMSE values created from this LASSO model. We can see unfortunately these are overall higher and farther apart. It is still better than the null model.

```{r figure 2.9,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/Pred_vs_obs_value_lasso_test.png")
```

```{r figure 2.10,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/Resid_lasso_test.png")
```

Table 2.6
```{r table 2.6,  echo=FALSE}
tab26=readRDS("../../results/LASSO_rmse_train_tab.rds")
knitr::kable(tab26)

@@

@@

## Summary and Interpretation
_Summarize what you did, what you found and what it means._

## Strengths and Limitations
_Discuss what you perceive as strengths and limitations of your analysis._

## Conclusions
_What are the main take-home messages?_

>>>>

---
title: "MADA Project: COVID-19 Vaccinations and recovery"
subtitle: ""
author: Dawson Dobash
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

@@

[https://data.oecd.org/healthres/health-spending.htm](https://data.oecd.org/healthres/health-spending.htm)

[https://www.kaggle.com/iamsouravbanerjee/covid19-dataset-world-and-continent-wise?select=Covid+Data+-+World.csv](https://www.kaggle.com/iamsouravbanerjee/covid19-dataset-world-and-continent-wise?select=Covid+Data+-+World.csv)

[https://www.kaggle.com/anandhuh/latest-worldwide-vaccine-data](https://www.kaggle.com/anandhuh/latest-worldwide-vaccine-data)

[https://data.worldbank.org/indicator/NY.GDP.PCAP.CD](https://data.worldbank.org/indicator/NY.GDP.PCAP.CD)

[https://en.wikipedia.org/wiki/List_of_countries_by_system_of_government](https://en.wikipedia.org/wiki/List_of_countries_by_system_of_government)

@@

## Question 1: Difference in proportions of recovery and deaths

Table 1.1 displays the top five and bottom five death rates. Also within this, it shows their corresponding recovery rates as well. We can see that the bottom five death rates are from Asia but also the highest, Yemen, is also within the Asia continent as well. 
<br /> 
<br />

Table 1.1: Top 5 and bottom 5 death rates by country
```{r table1,  echo=FALSE}
tab1=readRDS("../../results/table3.rds")
knitr::kable(tab1)
```

@@

```{r figure 1.1, echo=FALSE}
knitr::include_graphics("../../results/prop_diff_recov_died.png")
```

@@

```{r figure 1.2, echo=FALSE}
knitr::include_graphics("../../results/log_prop_diff_hist.png")
```

@@

Using the logit transformation, I ran 4 simple linear regression models. Below I provide the statistics of one of the models within Tables 1.2.

@@

Table 1.2: Summary statistics for linear regression (logit transformation of prop diff of recovery and deaths vs. vaccine)
```{r table 1.2,  echo=FALSE}
tab2=readRDS("../../results/tablevacc1.rds")
knitr::kable(tab2)
```

Looking at Table 1.2, we can see that the R^2 values are very low. This is similar to all of the other simple linear regression models. The statistics for the other three models are within the supplemental material. Therefore none of these predictors shows any association with the logit transformation outcome. Since not even one predictor is good for this outcome, I am going to stop my analysis with this outcome and go to my second question which uses the percent of cases within each country.

## Question 2: Percent of people vaccinated for each country

### Methods

@@

### Exploratory Analysis

@@

Table 2.1: Top 5 and bottom 5 vaccination percentages by country
```{r table 2.1,  echo=FALSE}
tab21=readRDS("../../results/vacc_tab.rds")
knitr::kable(tab21)
```

@@

```{r figure 2.1, echo=FALSE}
knitr::include_graphics("../../results/vacc_hist.png")
```

When looking at Figure 2.2, we can see that those countries who have large values of GDP per capita, their population is more vaccinated. The vaccination number varies when the GDP per capita is relatively low.

```{r figure 2.2, echo=FALSE}
knitr::include_graphics("../../results/gdp_vs_vacc.png")
```

Looking at Figure 2.3, this side-by-side boxplot shows that Africa is significantly different to all of the other continents. Africa is historically known is a less developed continent. This could be result in lower supplies to Africa compared to other places in the world. Within the other continents, Europe seems to have th highest median vaccinated proportions.

```{r figure 2.3, echo=FALSE}
knitr::include_graphics("../../results/loc_vs_vacc.png")
```

Figure 2.4 is showing the logit transformation of the proportion of the population vaccinated. This is due to the skewness of the non-transformed vaccinatio numbers. We see that this is still skewed but its skewed left where most of the data is around that 0 value.

```{r figure 2.4, echo=FALSE}
knitr::include_graphics("../../results/log_vacc.png")
```

### Main Analysis

As specified within the methods section, the first part of my analysis will be comparing the RMSE of my full model to the null model. However, before I do this I will run a correlation matrix of the numeric variables to see if some variables are highly correlated.

In Table 2.2 we can see that the two variable, which I suspected, that are highly correlated are health care funds (Value) and GDP per capita. Since those two variables are highly correlated and the health care funds variable only includes 48 observations, I will remove health care funds out of the full model.

Table 2.2: Correlation martrix of predictors and outcome
```{r table 2.2,  echo=FALSE}
tab22=readRDS("../../results/cor_tab.rds")
knitr::kable(tab22)
```

@@

Table 2.3: Summary statistics for full model
```{r table 2.3,  echo=FALSE}
tab23=readRDS("../../results/Summ_stat_mult_reg.rds")
knitr::kable(tab23)

@@

Table 2.4: RMSE values for full model (training and test data, respectively)
```{r table 2.4,  echo=FALSE}
tab24=readRDS("../../results/Logit_vacc_rmse_tab.rds")
knitr::kable(tab24)
```

Table 2.5: RMSE values for null model (training and test data, respectively)
```{r table 2.5,  echo=FALSE}
tab25=readRDS("../../results/Logit_vacc_rmse_null_tab.rds")
knitr::kable(tab25)
```

@@

For the LASSO model, there is some preparation we need to run this. We will use cross validation to create the multiple models included in the LASSO model. This cross validation will be a 5-fold stratified by the outcome. We then, like previously, create a workflow using a specific model type and recipe. The recipe will be the full model recipe but the model type will be different. The LASSO model uses a specific model that has a tuning factor into a linear regression type. Once we have our workflow, we need to make a grid as the LASSO model created multiple models based on the 5-fold cross validation and other factors. From the workflow, we can apply a tuning grid to it. This will produce the variety of models. To find the best model, we an apply a function called show_best and specify RMSE to find the best model in terms of RMSE. After putting this model into a workflow and creating a fit object, we get the statistics of the best model.

Figure 2.5 shows the predicted values to the observed values. Most of the points follow the trend and there seems to show no pattern. We can see this more within Figure 2.6 which is the residual plot. Within Figure 2.6, we could see a slight pattern at the begging points where they are grouped up more.

```{r figure 2.5, echo=FALSE}
knitr::include_graphics("../../results/Pred_vs_obs_value_lasso_train.png")
```

```{r figure 2.6, echo=FALSE}
knitr::include_graphics("../../results/Resid_lasso_train.png")
```

The last part of the LASSO modeling analysis is fitting the model to the test data to see how well they both look together. To look at the test data results, we need to run a last fit function which just applies the test data to the best model found above. Figure 2.7 and Figure 2.8 show the predicted values versus observed and its residual plot for the test data. Just like the training test, most of the predicted values do have a similar trend and it close to the observed value. The residual plot shows that concerning line of observations for the lower values. This residual plot show more variability in the lower values more. Table 2.6 shows the RMSE values created from this LASSO model. We can see unfortunately these are overall higher compared to the full model numbers. It is still better than the null model however.

```{r figure 2.7, echo=FALSE}
knitr::include_graphics("../../results/Pred_vs_obs_value_lasso_test.png")
```

```{r figure 2.8, echo=FALSE}
knitr::include_graphics("../../results/Resid_lasso_test.png")
```

Table 2.6: Comparing RMSE for training and test split data for LASSO model, respectively 
```{r table 2.6,  echo=FALSE}
tab26=readRDS("../../results/LASSO_rmse_train_tab.rds")
knitr::kable(tab26)

@@

This is the product from the LASSO modeling. This is the model produced by LASSO. In Table 2.7, we can see there are 4 predictors and 2 were removed. The predictors that were removed was the proportion of those who died in each country and test per person. However these estimates are based on the logit transformation of our outcome. The last column is the transformation to display the transformed of each predictor applying the exp() function to the estimates.

From the estimates, we can see although there was 2 variables that suppressed to a value of 0 based on the LASSO model, the predictor gdp per capita have roughly a value of 0 which translates to a odds ratio close to 1. Those who include 1 or close to 1 results in a non-significant variable in predicting the outcome. We can see the continent that the country is in also has an affect on proportion vaccinated where the continent Africa is the reference group. The continents that increases the proportion of being vaccinated the most are Asia and South America. We can also see that in terms of government type where a republic government is the reference group, those countries that are a monarchy increase the proportion of having more vaccinations. In opposite affect, a provisional government country lowers the proportion of getting people vaccinated.

Table 2.7: Summary statistics of LASSO model and predictors with their respected transformed values 
```{r table 2.7,  echo=FALSE}
tab27=readRDS("../../results/transform_LASSO.rds")
knitr::kable(tab27)
```

@@

## Summary and Interpretation
The analysis was split up into two different analyses specified by the two questions. The first analysis was looking at the difference of proportions between recovery and death rates. With some exploratory analysis, no association according to the simple linear regression between multiple predictors and the outcome. Since within some exploratory analysis and very small r-square values, I decided to stop that analysis on the first question and go to the next question.

<\ br>

The second question pertains to vaccination proportions. Using the logit transformation and applying the LASSO modeling, out of the 6 predictors within the full model, only 4 remained within the equation. These include percent of cases for a country, gdp per capita, the continent the country resides, and the type of government. Out of these, those who have the most impact are location and government type, and gdp per capita has roughly an estimate of 0 which probably has no impact on the proportion of people vaccinated.

## Strengths and Limitations
Some strengths to this analysis was that since this topic of COVID-19 is in todays news which means much of the countries information is available in public use. Along with COIVD-19 information, most information of countries are of public use therefore lots of information  was easy to find.

Some limitations for this analysis was that I was using cumulative data which means as more days pass, this data will become old analyses. Another limitation was although I got the information I wanted, I had to use multiple sources to find them which results in combining data sets and ultimately errors.

## Conclusions
We find that due to high high recovery right is for most countries compared to death rates, and no predictors have a large association, according to the simple linear regression r-squared values, the difference in proportion between recovery and death rates is not affected by most predictors.

We see that the proportion of people vaccinated is associated with the amount of COVID-19 cases, which continent the country is in, and type of government. Given all other variable constant, Asia and South America gives the highest proportional increase compared to Africa, and monarchy governments increase vaccinations compared to republic government countries.

### 2021-11-28 products/manuscript/Supplemental Material.Rmd
MADA project part 5 (no references yet)

---
title: "MADA Project: Supplemental Material"
subtitle: ""
author: Dawson Dobash
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

A table summarizing the data.

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Data summary table.')
```

A table of the top 10 countries with the highest percentage of cases by population. We can see that there are a variety of locations and that Montenegro and Czech Republic are the highest 2 countries with the most cases by population.

```{r table1,  echo=FALSE}
tab1=readRDS("../../results/table1.rds")
knitr::kable(tab1)
```

A table of the top 5 and bottom 5 recovery rates also sharing the total cases numbers.It looks that Asia dominates the top 5 countries for recovery rate. For the bottom 5, there is a mixture of locations. We can also see that the recovery rate and death rate for the bottom 5 teams do not add up to 100 or close to it. This means there are a lot of active cases.

```{r table2,  echo=FALSE}
tab2=readRDS("../../results/table2.rds")
knitr::kable(tab2)
```

A table  of the top 5 and bottom 5 countries for death rate. We can see that Vanuatu only has a total of 4 cases but Yemen also has a significantly large rate then the next top country, Mexico. We can also see that Asia dominates the lowest death rates.

```{r table3,  echo=FALSE}
tab3=readRDS("../../results/table3.rds")
knitr::kable(tab3)
```

A scatterplot figure  of total cases by population. United States, India, and Brazil are some outliers of the countries.

```{r figure1,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/figure1.png")
```

A scatterplot figure of total cases by population filtered down to countries with less than 40 million population. We can see that the total cases are spread out.

```{r figure2,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/figure2.png")
```

A scatterplot figure of total recovered patients by total cases. We can see just like in figure 1 that the United States, India, and Brazil have a overwhelmingly more cases than other countries. Therefore in figure 4, we will explore the majority of the countries.

```{r figure3,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/figure3.png")
```

A scatterplot figure of the same plot as before just filtering countries with less than 20 million cases. We can see a linear relationship between the recovered to total cases. It looks like a slope of 1.

```{r figure4,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/figure4.png")
```

A scatterplot figure of percent of people fully vaccinated by health care funding. We can see that it is a linear relationship with a positive correlation. We can also see that the United States is out of the norm where they spend a lot more on health care funding compared to the percent of people fully vaccinated.

```{r figure6,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/figure6.png")
```

A histogram figure of the percentage of cases per population. We can see that this data is highly skewed to the right.

```{r figure8,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/figure8.png")
```

We can see with looking at figure 5 that the percentage of cases are roughly bimodal or even right skewed. For now, I will proceed with doing some simple linear regression. Below shows model statistics for each model and a visual showing the relationship between the two variables.

Figure 10 is showing statistics for the predictor percentage of cases.
```{r vaccine pct,  echo=FALSE}
knitr::include_graphics("../../results/figure10.png")

tab9=readRDS("../../results/tablepctcases2.rds")
knitr::kable(tab9)
```

Figure 11 is showing statistics for the predictor health care funds.
```{r health care,  echo=FALSE}
knitr::include_graphics("../../results/figure11.png")

tab10=readRDS("../../results/tablehc2.rds")
knitr::kable(tab10)
```

Figure 12 is showing statistics for the predictor number of tests per person.
```{r Tests,  echo=FALSE}
knitr::include_graphics("../../results/figure12.png")

tab11=readRDS("../../results/tabletests2.rds")
knitr::kable(tab11)
```

Figure 13 is showing statistics for the predictor location which specifies the continent for each country.
```{r Location,  echo=FALSE}
knitr::include_graphics("../../results/figure13.png")

tab12=readRDS("../../results/tableloc2.rds")
knitr::kable(tab12)
```

>>>>

---
title: "MADA Project: Supplemental Material"
subtitle: ""
author: Dawson Dobash
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---
This document displays some supplemental material to the analysis.

**Supplemental material for question 1**

This table is showing statistics for the simple linear regression between the predictor health care funds with the outcome being the logit transformation of the proportional difference between recovery and death rates. This is supplemented for table 1.2.

This helps describe that no predictors are good in predicting the outcome with a low R-squared.

```{r table regr for hc,  echo=FALSE}
tab3=readRDS("../../results/supp_mat/tablehc1.rds")
knitr::kable(tab3)
```

This table is showing statistics for the simple linear regression between the predictor number of tests performed with the outcome being the logit transformation of the proportional difference between recovery and death rates. This is supplemented for table 1.2.

This helps describe that no predictors are good in predicting the outcome with a low R-squared.

```{r table regr for tests,  echo=FALSE}
tab4=readRDS("../../results/supp_mat/tabletests1.rds")
knitr::kable(tab4)
```

This table is showing statistics for the simple linear regression between the predictor location, which is the continent each country is associated with, with the outcome being the logit transformation of the proportional difference between recovery and death rates. This is supplemented for table 1.2.

This helps describe that no predictors are good in predicting the outcome with a low R-squared.

```{r table regr for loc,  echo=FALSE}
tab5=readRDS("../../results/supp_mat/tableloc1.rds")
knitr::kable(tab5)
```

**Supplemental material for question 2**

This table is showing statistics for the simple linear regression between the predictor percentage of cases with the outcome being the logit transformation of the proportion of people vaccinated.

```{r vaccine pct,  echo=FALSE}
tab9=readRDS("../../results/supp_mat/tablepctcases2.rds")
knitr::kable(tab9)
```

This table is showing statistics for the simple linear regression between the predictor GDP per capita with the outcome being the logit transformation of the proportion of people vaccinated.

```{r health care,  echo=FALSE}
tab10=readRDS("../../results/supp_mat/tablegdp2.rds")
knitr::kable(tab10)
```

This table is showing statistics for the simple linear regression between the predictor number of COVID-19 tests per person with the outcome being the logit transformation of the proportion of people vaccinated.

```{r Tests,  echo=FALSE}
tab11=readRDS("../../results/supp_mat/tabletests2.rds")
knitr::kable(tab11)
```

This table is showing statistics for the simple linear regression between the predictor location which is the continent with the outcome being the logit transformation of the proportion of people vaccinated.

```{r Location,  echo=FALSE}
tab12=readRDS("../../results/supp_mat/tableloc2.rds")
knitr::kable(tab12)
```

This figure shows that there is no trend between vaccinations and cases until you get out to over 10% of the population had cases of COVID-19. The vaccination numbers range a lot when there is a low perecentage of cases compared to the countries population.

```{r case vs vacc, echo=FALSE}
knitr::include_graphics("../../results/supp_mat/cases_vs_vacc.png")
```

This figure shows the tuning process in a visual. The best model is represented by the lowest RMSE within the dip.

```{r tune process, echo=FALSE}
knitr::include_graphics("../../results/supp_mat/lasso_tune_process.png")
```
